Notes of Preskill's Quantum Information Theory

### 2016-09-08 Finished/Physical Challenges of Quantum Computation/Physical_CoQC.tex
Daily update. Too many things to be covered.

\title{Notes of Gravity and Entanglement}
\date{\today}
\author{Taper}

@@

\maketitle
\abstract{
This is my notes to \cite{utube_video}, a video lecture given by
professor Mark Van Raamsdonk. Also, it seems that this lecture is
unrelated to another paper of the same title, written by the same
author, on arXiv \cite{arxiv_paper}.
}
\tableofcontents

\section{Lecture}
\label{sec:Lecture}

We have reviewed ads/CFT, entanglement, some interesting connections
between entanglement structure of the CFT states, and the geometry
structure of the space time due to this state. If this is true, a natural
question is whether we can understand spacetime dynamics, i.e. gravitation,
from some physics related to entanglement.

Consider some CFT theory, assumning to satisfy the xxxxx (1'50) conjectur 
entanglement entropies are computed via:
xxxxx conjecture
2'17

\begin{align}
    S(A) = \frac{\text{Area}(\title{A})}{4G_N}
\end{align}

Some propertries that entanglement entropy must satisfy:
\begin{enumerate}
    \item sub-aditivity: $S(A and B)-S(A)-S(B) \geq 0$
\end{enumerate}
If there is some geometry due to the original states, will their entropy
statisfy the above constraints. Hence: \textbf{what do those constraints imply about
the spacetime geometry?}

Start with small perturbations to (?). 
\begin{thebibliography}{1}
    \bibitem{utube_video} Availalble on Youtube: \href{https://www.youtube.com/watch?v=ABJvMg5d9OY}{Mark Van Raamsdonk -Gravity and Entanglement}.
    \bibitem{arxiv_paper} \href{http://arxiv.org/abs/1609.00026v1}{arXiv:1609.00026v1}
\end{thebibliography}
\printnomenclature
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}

>>>>

\title{Notes of Physical Challenges of Quantum Computation}
\date{\today}
\author{Taper}

@@

\maketitle
\abstract{
    This is a note to the dissertation \cite{dissertation} by professor MH Wong in SUSTC.
}
\tableofcontents
\section{Chapter 1 Overview}
\label{sec:Chapter_1_Overview}

    \subsection{1.1 Introduction to quantum computing}
    \label{sec:1.1_Introduction_to_quantum_computing}
    Here he presents some differences between the classical and quantum
    computers. Keywords: \textbf{quantum parallelism}, \textbf{reversible
    computation process}, \textbf{simulation of quantum dynamics}.

    \subsection{1.2~1.3 Physical implementations and challenges 
    of quantum computing}

    These two parts do as the title suggests. The methods are summarized
    in the following table:

    \begin{table}[H]
    \centering
    \caption{Different Quantum Computing Approaches}
    %\label{my-label}

    \begin{tabular}
        {|p{\dimexpr0.333\textwidth-2\tabcolsep-\arrayrulewidth\relax}|
         p{\dimexpr0.333\textwidth-2\tabcolsep-\arrayrulewidth\relax}|
         p{\dimexpr0.333\textwidth-2\tabcolsep-\arrayrulewidth\relax}|
        }
        %{lll}
    \multicolumn{1}{c}{Name} & \multicolumn{1}{c}{Method} & \multicolumn{1}{c}{Error Prevention} \\ \hline
        gate model 
            & $U\ket{\text{Input}}=\ket{\text{Output}}$ 
            & quantum error correction, 
              analogous to its classical counterparts. \\ \hline
        adiabatic model 
            & Keep the quantum states of qbits in ground state. 
            & Prevent thermalization. \\ \hline
        one-way quantum computing/measurement-based quantum computing 
            & Initialized in cluster state. Computation achived via 
              a series of adaptive measurements. 
            & High quality cluster state. Precision in measurement.
        \\ \hline
    \end{tabular}

    \end{table}

    It should be noted that the above classification is not exclusive,
    there are certainly overlap between the three approaches. 
\begin{thebibliography}{1}
    \bibitem{dissertation} From UIUC:
    \url{https://www.ideals.illinois.edu/bitstream/handle/2142/14565/yung_manhong.pdf?sequence=1&isAllowed=y}
\end{thebibliography}
\printnomenclature
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}

### 2016-09-08 G.R/G.R.tex
Daily update. Too many things to be covered.

The Landau's book\cite{landau}, introduces a

\begin{thebibliography}{1}
    \bibitem{landau} The Classical Theory of Fields
\end{thebibliography}
\printnomenclature
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}

>>>>

    To do dynamics, we necessarily need a measure of distance. 
    Here introduces the distance in spacetime - interval. It is:
    \begin{align}
        \diff s^2 = \diff t^2 - \diff x^2 - \diff y^2 - \diff z^2
    \end{align}
    \textbf{Note} that from now on, I will try to use natural units
    as often as possible.

    Such a measure should be invariant in different Lorentz frames.
    Landau proves it by postulating a priori that:
    \begin{align}
        \diff s^2 = a \diff s'^2
    \end{align}
    This is suggested by $\diff s=0$ is invariant (invariance of the
    speed of light), and $\diff s$ and $\diff s'$ should be 
    infinitesimals of the same order. From this postulation, it is
    straightforward to argue that $a$ should be a constant and is
    equal to $1$.

    Using this property, one can classify interval between events
    as being \textit{timelike, spacelike,} and \textit{lightlike},
    by whether $ds>0$, $ds<0$ or $ds=0$. A mnemonic tip is that
    for timelike intervals, the "time difference" is dominant,
    and for spacelike intervals, the spatial difference is
    dominant.

    The following figure gives an indication of how the timelike,
    spacelike, lightlike classification is related to causality:
    \begin{figure}[H]
        \centering
        \includegraphics[width=0.6\linewidth]{pics/{ch1.spacetime_regions}.png}
        \caption{Spacetime regions}
    \end{figure}

    Only those events in the absolute future and in the absolute past
    regions can have a causal link with the people at $O$, due to the 
    limit of speed of propagation. And the future and past combined
    together as the timelike region.

    Another difference of timelike and spacelike regions lies in the
    prefix "absoluate". All events in timelike region cannot be
    simultaneous with $O$ in any reference frame, since the interval
    must have a nonzero time component. Similarly all events in
    spacelike region must happen in different place with the $O$.
    An additional requirement, which comes naturally from law of
    causality, is that all events in the future must remain absolutely
    in the future in any reference frame. Similarly we have an
    absolute past.

    Interestingly, the concept of being simultaneous with $O$, 
    being before or after $O$ in time, are relative for events in
    spacelike region. However, since there can be no causal link
    between $O$ and those events, this relativity does not pose
    a challenge to causality.

    Lastly, the cone formed by all events with $ds=0$ is called the
    \textit{light cone}. Events in it is very special that it deserve
    to devote a separate section to discuss it, which will be done
    later in this note.

    \subsection{Proper Time}
    \label{sec:Proper_Time}

    By
    \begin{align*}
        dt'^2 = dt^2-dx^2 = dt^2-(v\diff t)^2
    \end{align*}
    we have 
    \begin{align}
        \label{eq:}
        \Delta t' = \int_{t_1}^{t_2} \diff t \sqrt{1-v^2}
    \end{align}

    This shows the time dilation effect of a moving clock.
    Also, by this we can always calculate the time experienced by a clock
    by $t=\frac{1}{c}\int\diff s$ (SI unit).

    The Landau's book \cite{landau} explains a classical paradox about
    time dilation, which is omitted here.

    Interestingly, we have the property that, for all lines between two
    events, the longest one (i.e. the path that has the longest interval),
    is the straight line, contrary to the classical case. To see this,
    we note that any two events (assumed to be causally linked) can be
    connected by a flying clock with uniform speed.

    \subsection{Light's life}
    \label{sec:Lights_life}
    The life of a proton must be miserable.

    Possible sources: \href{http://physics.stackexchange.com/questions/16018/does-a-photon-in-vacuum-have-a-rest-frame}{1},
    \href{http://physics.stackexchange.com/questions/29082/would-time-freeze-if-you-could-travel-at-the-speed-of-light}{2}.
    \href{https://www.quora.com/What-does-the-frame-of-reference-of-a-photon-look-like}{3}.
\begin{thebibliography}{1}
    \bibitem{landau} The Classical Theory of Fields
\end{thebibliography}
\printnomenclature
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}

### 2016-09-08 Green function/green-f.tex
Daily update. Too many things to be covered.

    Therefore, the result is something like:
    \begin{align}
        t^x_{nm}=-t e^{i2\pi\sum_{m'<m}\Phi_{nm'}/\Phi_0}
    \end{align}
\printnomenclature
    \subsection{3.2 Including spin degrees of freedom}
    \label{sec:3.2_Including_spin_degrees_of_freedom}

@@

    Here it is mentioned than the transmission coefficient is related
    Green's funciton in the following way:
    \begin{align}
        T_{pq} = \text{Tr}\left[\Gamma_p G_{pq}\Gamma_q G^{\dagger}_{pq}
                \right]
    \end{align}
    Here $G_{pq}$ is, to borrow the language of matrix mechanics,
    a submatrix of the Green's function. $\Gamma_p$ is a abbreviation
    for the following counting:
    \marginpar{I am not sure about this peculiar thing.}
    \begin{align}
        \label{eq:}
        \Gamma_p \equiv i(\sum_p-\sum^\dagger_p)
    \end{align}
    Here $\sum_p$ is named "self-energy of the lead", something I
    don't quite understand.
\section{Anchor}

\begin{thebibliography}{1}
    \bibitem{dissertation} 
        \href{https://sundoc.bibliothek.uni-halle.de/diss-online/07/07H039/prom.pdf}{Electronic Transport in Mesoscopic Systems}, 
        by von Georgo Metalidis. (Link found via Google)
\end{thebibliography}
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}

>>>>

  Therefore, the result is something like:
  \begin{align}
      t^x_{nm}=-t e^{i2\pi\sum_{m'<m}\Phi_{nm'}/\Phi_0}
  \end{align}
  \subsection{3.2 Including spin degrees of freedom}
  \label{sec:3.2_Including_spin_degrees_of_freedom}

@@

  Here it is mentioned than the transmission coefficient is related
  Green's funciton in the following way:
  \begin{align}
      T_{pq} = \text{Tr}\left[\Gamma_p G_{pq}\Gamma_q G^{\dagger}_{pq}
              \right]
  \end{align}
  Here $G_{pq}$ is, to borrow the language of matrix mechanics,
  a submatrix of the Green's function. $\Gamma_p$ is a abbreviation
  for the following counting:
  \marginpar{I am not sure about this peculiar thing.}
  \begin{align}
      \label{eq:}
      \Gamma_p \equiv i(\textstyle\sum_p-\textstyle\sum^\dagger_p)
  \end{align}
  Here $\sum_p$ is named "self-energy of the lead", something I
  don't quite understand.
  \subsection{4.3 Lattice Green’s function method}
  \label{sec:4.3_Lattice_Greens_function_method}
  In this section, the author builds up a recursive method to calculate
  the Green's function. The difficulty in calculating Green's function
  is that the Hamiltonian matrix might be infinite, hence impossible
  to invert numerically, or the inversion is numercially expensive.
  Hence a recursive method is more preferable.

  We define a notation for one particular submatrix of Green's funciton.
  $G_{nn'}$ is such that:
  \begin{align}
      \braket{m,\sigma|G_{nn'}(E)|m',\sigma'} 
          \equiv \braket{nm\sigma |G(E)|n'm'\sigma'}
          = G_{nm\sigma,n'm'\sigma'}(E)
  \end{align}
  where $(m,n)$ labels columns in the tight-binding lattice, 
  and $\sigma$ is the spin index.

    \subsubsection{4.3.1 Semiinfinite leads: Self-energy description}
    \label{sec:4.3.1_Semiinfinite_leads_Self-energy_description}
    We have the following Hamiltonian from Landauer-Büttiker 
    formalism,
    \begin{align}
        H= H_{cd} + \sum_i (H^i_l + V^i_{ld} + V^i_{dl})
        \label{eq:ch4.1.3_H_general}
    \end{align}

    where $H_{cd}$ is the Hamiltonian for the central device, and 
    $H_{li}$ the Hamiltonian for lead $i$. The coupling between 
    lead and device is described by $V_{ld}^i$ (and its hermitian
    conjugate $V_{dl}^i$ ).

    Here is a improvement on that. 
    It is shown that the central device, including the influence of
    leads on it, is described by a \textit{finite-dimensional}
    Hamiltonian:
    \begin{align}
        \mathcal{H}_{cd} = H_{cd} + \sum_i \textstyle\sum^i
    \end{align}
    where $\sum^i$ is called the retarted self-energy of lead $i$:
    \begin{align}
        \textstyle\sum^i = V^i_{dl}g^i_l V^i_{ld}
    \end{align}
    Here $g^i_l$ is the Green's function of the isolated 
    semi-infinite lead: $g^i_l= [E+i\eta -H^i_l]^{-1}$.

    At this point, the problem of computation is finally solve 
    because we are using nearest neighbour model here. Hence the 
    dimension of some matrix is significantly cut down.
    \marginpar{
        Actually, I don't see why the dimension of matrix is infinite
        in the above \ref{eq:ch4.1.3_H_general}, while here the
        matrix suddenly become fininte.
    }
    Also, author mentions that several methods are available to
    calculate this Green's funciton: analytical solution when the
    magnetic field is absent; numerical methods when there is a
    magnetic field.

    \subsubsection{4.3.2 Recursive technique: Standard method}
    \label{sec:4.3.2_Recursive_technique_Standard_method}
    Recursive method is based on the Dyson's equation:
    \begin{align}
      \label{eq:4.3.2.Dyson_Equaton}
      \hat{G}=\hat{g}+ \hat{g} \hat{V}\hat{G}
    \end{align}
    (Note that this is an equation of operators!)

    Here $g$ is the Green's function of two disconnected subsystems,
    $G$ is the Green's funciton of the connected system,
    comprising two previously disconnected subsystems; $V$ describes
    the hopping between the subsystems. One may already see the
    spirit of recursive method, by that $G$ appears on both side
    of the equation.

    It should be noted that, strictly speaking, in Dyson's equation
    there should be two part: the self-energy part and everything
    else (categorized as external potential). But I am not confident
    about this.
    % TODO improve Dyson's equation.

    After this, the author illustrate one simple example of using
    Dyson's equation to calculate $G$.
\section{Anchor}

\begin{thebibliography}{1}
    \bibitem{dissertation} 
        \href{https://sundoc.bibliothek.uni-halle.de/diss-online/07/07H039/prom.pdf}{Electronic Transport in Mesoscopic Systems}, 
        by von Georgo Metalidis. (Link found via Google)
\end{thebibliography}
\printnomenclature
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}

### 2016-09-08 Quantum Information/preskill.tex
Daily update. Too many things to be covered.

\title{Notes of Physical Challenges of Quantum Computation}
\date{\today}
\author{Taper}

@@

\maketitle
\abstract{
    This is a note to the dissertation \cite{dissertation} by professor MH Wong in SUSTC.
}
\tableofcontents
\section{Chapter 1 Overview}
\label{sec:Chapter_1_Overview}

    \subsection{1.1 Introduction to quantum computing}
    \label{sec:1.1_Introduction_to_quantum_computing}
    Here he presents some differences between the classical and quantum
    computers. Keywords: \textbf{quantum parallelism}, \textbf{reversible
    computation process}, \textbf{simulation of quantum dynamics}.

    \subsection{1.2~1.3 Physical implementations and challenges 
    of quantum computing}

    These two parts do as the title suggests. The methods are summarized
    in the following table:

    \begin{table}[H]
    \centering
    \caption{Different Quantum Computing Approaches}
    %\label{my-label}

    \begin{tabular}
        {|p{\dimexpr0.333\textwidth-2\tabcolsep-\arrayrulewidth\relax}|
         p{\dimexpr0.333\textwidth-2\tabcolsep-\arrayrulewidth\relax}|
         p{\dimexpr0.333\textwidth-2\tabcolsep-\arrayrulewidth\relax}|
        }
        %{lll}
    \multicolumn{1}{c}{Name} & \multicolumn{1}{c}{Method} & \multicolumn{1}{c}{Error Prevention} \\ \hline
        gate model 
            & $U\ket{\text{Input}}=\ket{\text{Output}}$ 
            & quantum error correction, 
              analogous to its classical counterparts. \\ \hline
        adiabatic model 
            & Keep the quantum states of qbits in ground state. 
            & Prevent thermalization. \\ \hline
        one-way quantum computing/measurement-based quantum computing 
            & Initialized in cluster state. Computation achived via 
              a series of adaptive measurements. 
            & High quality cluster state. Precision in measurement.
        \\ \hline
    \end{tabular}

    \end{table}

    It should be noted that the above classification is not exclusive,
    there are certainly overlap between the three approaches. 
\begin{thebibliography}{1}
    \bibitem{dissertation} From UIUC:
    \url{https://www.ideals.illinois.edu/bitstream/handle/2142/14565/yung_manhong.pdf?sequence=1&isAllowed=y}
\end{thebibliography}
\printnomenclature
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}

>>>>

\title{Notes of Preskill's Quantum Information Theory}
\date{\today}
\author{Taper}

@@

\maketitle
\abstract{
This is a note taken when I read the course notes of Preskill's
course on quantum computation.
}
\tableofcontents
\section{Chapter 2 Foundations I: States and Ensembles}
\label{sec:Chapter_2_Foundations_I_States_and_Ensembles}

    \subsection{2.2 The Qubit}
    \label{sec:2.2_The_Qubit}
    Here the concept of qubit is defined:
    \begin{defi}[Qubit]
    \nomenclature{Qubit}{\nomrefpage.}
        A qubit is a quantum system described by a two-dimensional 
        Hilbert space.
    \end{defi}
    However, since measurement collapse the superposition state of quantum
    mechanics, there seems to be not difference between a qubit and a 
    classical bit whose initial state is only known probabilistically.
    More important distinction should be and will be pointed out in the
    next few sections.

    \paragraph{Spin-$\frac{1}{2}$}

\begin{thebibliography}{1}
    %\bibitem{book} 
\end{thebibliography}
\printnomenclature
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}
